Figures

### 2020-01-09 figures/01_geometry.Rmd
add geometry figures

```{r 01_hypsography, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}

ids <- factor(c("convex", "concave"))
polys <- data.frame(
  id = rep(ids, each = 3),
  x = c(0, 100, 0, 
        0, 100, 100), 
  y = c(100, 0, 0, 
        100, 100, 0))

dt_raw <- read.csv("../data/00_hypso/hypso.csv", stringsAsFactors = FALSE)

ggplot(data = dt_raw) +
  geom_polygon(data = polys, aes(x = x, y = y, group = id, fill = id), alpha = 0.2) +
  geom_line(aes(x = area_percent, y = depth_percent, group = llid)) +
  geom_abline(intercept = -100, slope = 1, color = "red") +
  ylim(c(100, 0)) +
  ylab("Depth (percent)") + xlab("Area (percent)") + 
  ggtitle(paste0("Normalized hypsography for ", length(unique(dt_raw$llid)), " lakes")) + 
  theme(legend.position = c(0.84, 0.2), 
        legend.title = element_blank()) +
  facet_wrap(~state)

>>>>

```{r 01_geometry, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
# example map of true deepest point versus visual center

dt <- readRDS("../data/00_bathy_depth/bathy_pnts.rds")

# plot of true deepest versus visual centers

(gg_test <- ggplot(data = st_drop_geometry(dt)) + 
  geom_point(aes(x = dist_deepest, y = dist_viscenter)) + # , color = llid)) +
  geom_abline(aes(intercept = 0, slope = 1)) +
  xlab("Distance to shore from deepest point") +
  ylab("Distance to shore from visual center"))

# plotly::ggplotly(gg_test)
# plot(res$dist_deepest, res$dist_viscenter)

get_pnt_map <- function(x){
  # x <- 3
  lg_example <- LAGOSUSgis::query_gis(
    "LAGOS_US_All_Lakes_1ha", "lagoslakeid", dt$llid[x])
  crs_example <- st_crs(
    raster(list.files(paste0("../data/", tolower(dt$state[x]), "_bathy"), 
               include.dirs = TRUE, full.names = TRUE)[1])
    )
  st_crs(dt$pnt_deepest)   <- crs_example
  st_crs(dt$pnt_viscenter) <- crs_example

  ggplot() + 
    geom_sf(data = lg_example) +
    geom_sf(data = dt$pnt_deepest[x], color = "red") + 
    geom_sf(data = dt$pnt_viscenter[x], color = "green") +
    theme_void()
}

# which(dt$llid == 5636)
# which(dt$llid == 257862)
# get_pnt_map(2352)
cowplot::plot_grid(get_pnt_map(which(dt$llid == 3791)) +
                     ggtitle(3791), 
                   get_pnt_map(which(dt$llid == 2772)) +
                     ggtitle(2772), 
                   get_pnt_map(which(dt$llid == 2655)) +
                     ggtitle(2655), 
                   get_pnt_map(which(dt$llid == 1822)) +
                     ggtitle(1822)
                   )

### 2020-01-09 manuscript/figures.Rmd
add messager equation table
add geometry figures

>>>>

![Messager et al. 2016 equation table](../figures/messager_eq_table.png){width=100%}

```{r 01_geometry_points, fig.cap = "Caption.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_geometry-1.pdf")
```

```{r 01_geometry_map, fig.cap = "Green points show the 'visual center' of the lake. Red points show the true deepest point of a lake.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_geometry-2.pdf")
```
